---
title: "Business and Biopdiversity - Ch 4 - Snowball Pilot"
format:
    html:
        toc: true
        toc-depth: 2
        embed-resources: true
        code-fold: true
        code-summary: "Show the code"
    docx:
        toc: true
        toc-depth: 2
        number-sections: true
        highlight-style: github
    pdf:
        toc: true
        toc-depth: 2
        number-sections: true
---

# Setup
```{r}
#| label: setup
#|

# library(bibtex)
library(openalexR)
library(writexl)
library(tibble)
library(dplyr)
library(ggplot2)
library(ggraph)
library(tidygraph)

library(knitr)

list.files(
    "R",
    full.names = TRUE,
    recursive = TRUE
) |>
    sapply(
        FUN <- source
    )


kp <- read.csv(file.path("Key Papers", "Ch 4 - Snowball Pilot.csv"))
```

# Searches

## OpenAlex

### Setup OpelAnex usage and do snowball serarch

```{r}
#| label: openalex_prep
#|

key_works <- oa_fetch(
    entity = "works",
    doi = kp$DOI,
    verbose = FALSE
)



saveRDS(key_works, file.path("data", "key_works.rds"))

ids <- openalexR:::shorten_oaid(key_works$id)

fn <- file.path(".", "data", "snowball.rds")
if (file.exists(fn)) {
    snowball <- readRDS(fn)
} else {
    snowball <- oa_snowball(
        identifier = ids,
        verbose = FALSE
    )
    saveRDS(snowball, fn)
}

flat_snow <- snowball2df(snowball) |>
    as_tibble()
```

### Save snowball as Excel file (`snowball_excel.xlsx`)

```{r}
#| label: openalex_excel
#|

###

fn <- file.path(".", "data", "snowball.xlsx")
to_xlsx(
    snowball = snowball,
    flat_snow = flat_snow,
    xls_filename = fn
)
```

The column are: (the Concept columns are not that relevant at the moment)

- **id**: internal id fromOpenAlex
- **author**: authors of the paper
- **publication_year**: publication year
- **title**: title of the paper
- **doi**: doi of the paper
- **no_referenced_works**: number of references in the paper which are also in OpenAlex
- **cited_global**: Number of times the paper has been cited
- **cited_global_per_year**: standardised  number of times cirted (cited_global / number of years published)
- **no_connections**: number of connections in the rgaph, i.e. either cited or citing a paper in the snowball corpus
- **concepts_l0**: Concept 0. level assigned by OpenAlex
- **concepts_l1**: Concept 1. level assigned by OpenAlex
- **concepts_l2**: Concept 2. level assigned by OpenAlex
- **concepts_l3**: Concept 3. level assigned by OpenAlex
- **concepts_l4**: Concept 4. level assigned by OpenAlex
- **concepts_l5**: Concept 5. level assigned by OpenAlex
- **author_institute**: Institute of the authors
- **institute_country**: Country of the institute
- **abstract**: the abstract of the paper


### Graph of links between references

```{r}
#| label: openalex_graph
#|
plot_snowball(
    snowball,
    name = "Snowball Pilot"
)
```

### Identification of references with more than one edge

This is the number of connections (`connection_count)`of the paper (`id`)

```{r}
#| label: openalex_edgecount
#|
mult_edge <- flat_snow |>
    select(id, connection_count) |>
    filter(connection_count > 1) |>
    arrange(desc(connection_count))

links <- flat_snow |>
    filter(id %in% mult_edge$id)

links |>
    select(id, display_name, publication_year, doi, connection_count) |>
    arrange(desc(connection_count)) |>
    knitr::kable()
```



# Finalize
To convert to pdf run e.g.

```{bash}
#| eval: false
    wkhtmltopdf snowball.html snowball.pdf
```
